Manuscript

### 2023-05-26 Manuscript1.Rmd
updates

```{r parameters visualization, fig.height=10, fig.width=12}
dd = get_experiment()

@@

layout = (c(
  area(1, 1),
  area(1, 2),
  area(2, 1),
  area(2, 2)

trial_struc = ggdraw() +
  draw_image(magick::image_read(here::here("figures", "main-experiment.PNG")), scale = 1.5)

trial_struc+kalmanplot+rwplot+wbplot+plot_layout(design = layout)+plot_annotation(tag_levels = 'A')

#RW_logistic = RW_logistic_vis(dd)
```

@@

mu_alpha = rep(0.2,100)
kappa_alpha = 50
mu_w1 = 0.2
kappa_w1 = 50
mu_w2 = 0.2
kappa_w2 = 50
sd_percept_precision = 0.5
sd_beta = 0.5
nsubs = 10
parameters = expand.grid(nsubs = nsubs, 
                         mu_alpha = mu_alpha, 
                         kappa_alpha = kappa_alpha, 
                         mu_w1 =  mu_w1, kappa_w1 = kappa_w1,
                         mu_w2 = mu_w2, kappa_w2 = kappa_w2, 
                         sd_percept_precision = sd_percept_precision, 
                         sd_beta = sd_beta)
parameters$id = 1:nrow(parameters)
data_list_wb <- split(parameters, parameters$id)

@@

@@

data_list = data_list_rw[1:5]

@@

data_list = data_list_wb[1:100]

plan(multisession, workers = 10)

@@

data_list = data_list_kalman[1]

@@

<!-- ```{r fitting to real data tester hierachical RW seesion2} -->

<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
<!--   rename_all(tolower) %>% -->
<!--   filter(trial != 0) %>% -->
<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
<!--   mutate_all(replace_na, 0) -->

<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->

<!-- df = df %>% filter(session == 2) -->

<!-- #source(here::here("stan_functions.R")) -->
<!-- #fitting hierachically -->
<!-- data = df %>% mutate(percept = percept/100) -->

<!-- data = data %>% mutate(across(percept, ~case_when( -->
<!--     . < 0.001 ~ 0.001, -->
<!--     . > 0.999 ~ 0.999, -->
<!--     TRUE ~ . -->
<!--   ))) -->

<!-- data2 = list(nsubs = length(unique(data$id)), -->
<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
<!--             pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
<!--             ) -->

<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->

<!-- rw_fit_ses2 <- mod$sample( -->
<!--       data = data2, -->
<!--       chains = 4, -->
<!--       parallel_chains = 4, -->
<!--       refresh = 100, -->
<!--       adapt_delta = 0.90, -->
<!--       max_treedepth = 12 -->
<!--     ) -->

<!-- ``` -->

>>>>

```{r parameters visualization, fig.height=14, fig.width=16}
dd = get_experiment()

@@

layout = (c(
  area(1, 1, 1,1),
  area(1, 2, 1,2),
  area(1, 3, 1,3)

))
plot(layout)

p1 = kalmanplot[[1]]+rwplot[[1]]+wbplot[[1]]+plot_layout(design = layout)+plot_annotation(tag_levels = list(c('B', 'C',"D","E","F","G")))
p2 = kalmanplot[[2]]+rwplot[[2]]+wbplot[[2]]+plot_layout(design = layout)+plot_annotation(tag_levels = list(c("E","F","G")))

p1
p2

RW_logistic = RW_logistic_vis(dd)
```

@@

mu_alpha = rep(0.3,100)
kappa_alpha = 50
mu_w1 = 0.3
kappa_w1 = 50
mu_w2 = 0.3
kappa_w2 = 50
sd_percept_precision = 0.5
sd_beta = 0.5
nsubs = 10
parameters = expand.grid(nsubs = nsubs, 
                         mu_alpha = mu_alpha, 
                         kappa_alpha = kappa_alpha, 
                         mu_w1 =  mu_w1, kappa_w1 = kappa_w1,
                         mu_w2 = mu_w2, kappa_w2 = kappa_w2, 
                         sd_percept_precision = sd_percept_precision, 
                         sd_beta = sd_beta)
parameters$id = 1:nrow(parameters)
data_list_wb <- split(parameters, parameters$id)

@@

mu_alpha = rep(0.3,100)
kappa_alpha = 50

mu_b1 = 2
sd_b1 = 1

mu_b2 = 2
sd_b2 = 1

data_list_logs <- split(parameters, parameters$id)

@@

data_list = data_list_rw

@@

data_list = data_list_wb

@@

data_list = data_list_logs

@@
